Supporting Information

### 2017-01-27 portfolio/text/anderson-etal-rev-pfx.tex
Order figs; edits

\newcommand{\tabstrategies}{1}
\newcommand{\figfe}{1}
\newcommand{\figre}{2}
\newcommand{\figspokeall}{3}
\newcommand{\figresid}{4}
\newcommand{\figresiddownside}{5}
\newcommand{\figstryrs}{6}
\newcommand{\figifq}{7}
\newcommand{\figmirror}{8}
\newcommand{\fignoeffort}{9}

@@

\begin{equation*}
  \begin{split}
\label{eq:mean}
\mu_{i,t} = \beta_{0,j,t} -
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} -\\
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1}),
  \end{split}
\end{equation*}

@@

\begin{equation*}
\begin{split}
\label{eq:cv}
\sigma_{i,t} =
\exp (\gamma_{0,j} -
\gamma_{1,j} S_{i,t} I_{i,t} +
\gamma_{2,j} S_{i,t} I_{i,t} +
\gamma_3 D_{i,t} -\\
\gamma_4 S_{i,t} D_{i,t} I_{i,t} +
\gamma_5 S_{i,t} D_{i,t} I_{i,t}).
\end{split}
\end{equation*}

@@

We fit our models with Stan 2.14.1 \cite{standevelopmentteam2016,
  standevelopmentteam2016a} and R 3.3.2 \cite{rcoreteam2016}. Stan implements
the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm \cite{hoffman2014}
to perform Bayesian statistical inference. We assigned weakly informative
priors on all parameters: \(N(0, 2^2)\) priors on all \(\beta\), \(\gamma\),
and \(\eta\) parameters, and half-\(t(3, 0, 2)\) priors (i.e.~degrees of
freedom of 3 and scale of 2) on all \(\sigma\) and \(\tau\). We ran four chains
and 2,000 iterations and discarded the first 1,000 iterations of each chain as
warm up. We checked for chain convergence visually with trace plots, ensured
that \(\hat{R}<1.05\) (the potential scale reduction factor) and that the
effective sample size, as calculated by the rstan R package
\cite{standevelopmentteam2016}, was greater than 200 for all parameters
\cite{gelman2014}. We verified that our model returned sensible estimates by
comparing our estimates to an ad-hoc two-stage model fit with the lme4 R
package \cite{bates2015}, where we first fit a mixed-effects regression model
to the mean, and then modelled the absolute residuals from that first model in
a second mixed-effects model representing the variance component. We also
validated the model with simulated data, and were able to recover the true
values (Supporting Information). Code used in our analysis is available at
\url{https://github.com/NCEAS/pfx-commercial/portfolios/}. } \showmatmethods

>>>>

\newcommand{\tabstrategies}{1}
\newcommand{\figspokeall}{1}
\newcommand{\figfe}{2}
\newcommand{\figre}{3}
\newcommand{\figmirror}{4}
\newcommand{\fignoeffort}{5}
\newcommand{\figifq}{6}
\newcommand{\figstryrs}{7}
\newcommand{\figresid}{8}
\newcommand{\figresiddownside}{9}

@@

\begin{equation}
  \begin{split}
\label{eq:mean}
\mu_{i,t} = \beta_{0,j,t} -
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} -\\
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1}),
  \end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
\label{eq:cv}
\sigma_{i,t} =
\exp (\gamma_{0,j} -
\gamma_{1,j} S_{i,t} I_{i,t} +
\gamma_{2,j} S_{i,t} I_{i,t} +
\gamma_3 D_{i,t} -\\
\gamma_4 S_{i,t} D_{i,t} I_{i,t} +
\gamma_5 S_{i,t} D_{i,t} I_{i,t}).
\end{split}
\end{equation}

@@

We fit our models with Stan 2.14.1 \cite{standevelopmentteam2016,
  standevelopmentteam2016a} and R 3.3.2 \cite{rcoreteam2016}. Stan implements
the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm \cite{hoffman2014}
to perform Bayesian statistical inference. We assigned weakly informative
priors on all parameters: \(N(0, 2^2)\) priors on all \(\beta\), \(\gamma\),
and \(\eta\) parameters, and half-\(t(3, 0, 2)\) priors (i.e.~degrees of
freedom of 3 and scale of 2) on all \(\sigma\) and \(\tau\). We ran four chains
and 2,000 iterations and discarded the first 1,000 iterations of each chain as
warm up. We checked for chain convergence visually with trace plots, ensured
that \(\hat{R}<1.05\) (the potential scale reduction factor), and that the
effective sample size, as calculated by the rstan R package
\cite{standevelopmentteam2016}, was greater than 200 for all parameters
\cite{gelman2014}. We verified that our model returned sensible estimates by
comparing our estimates to an ad-hoc two-stage model fit with the lme4 R
package \cite{bates2015}, where we first fit a mixed-effects regression model
to the mean, and then modelled the absolute residuals from that first model in
a second mixed-effects model representing the variance component. We also
validated the model with simulated data, and were able to recover the true
values (Supporting Information). Code used in our analysis is available at
\url{https://github.com/NCEAS/pfx-commercial/portfolios/}. } \showmatmethods

### 2017-01-27 portfolio/text/ms.Rmd
Order figs; edits

\label{fig:across}
\end{center}
\end{figure}

<!-- TODO AB: To me it is more intuitive that the darker, hotter colors would
represent higher values. Consdier reversing the color scale to go from red
(highest # of permit holders) to yellow (lowest #).  -->

@@

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given strategy (set of permits) is more variable
(Fig. \ref{fig:within}). After accounting for fishing effort and changes in
annual average revenue for fishers with the same set of permits, specializing
tends to be associated with increased revenue but also increased variability
(Fig. \ref{fig:within}; Figs S\figfe, S\figre, S\ref{fig:noeffort}).
 <!-- TODO LP: effort is endogenous? -->
On average, there is a ~0.5% increase in the year-to-year revenue ratio per 1%
decrease in species diversity, and across strategies weighted equally, `r
g2_dens`% of the probability density supports a positive relationship between
specialization and revenue.

@@

Changing (increasing or decreasing) an individual's fished species diversity 
within the constraints of a set of permits tends to be associated with greater 
expected variability or uncertainty in year-to-year revenue (Fig. 
\ref{fig:within} strategies above zero; Figs. S\figfe, S\figre, S\figmirror).
This effect was strongest for individuals with a halibut and sablefish permit. 
Individuals with this strategies experienced a ~2% increase in variability for a
1% change in the year-to-year ratio of species diversity (Fig.
\ref{fig:within}). Becoming more generalized in species diversity also leads to
increased revenue variability (Fig. S\ref{fig:mirror}A), suggesting that the act
of changing the number of species fished for a given set of permits is a
contributor to increased variability of revenue.

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery 
quota (IFQ) management in 1995, which potentially confounds our estimates with a
major regulatory change. Therefore, we refit our models allowing all 
strategy-level effects involving halibut and sablefish permits to vary 
separately before and after the introduction of IFQs. The introduction of IFQs 
was associated with a reduction in revenue variability of ~20--30% for
individuals with only halibut or sablefish permits (Fig. S\figifq A).
<!-- TODO AH: We need to note that the populatoin changed -->
Furthermore, for individuals within most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\figifq B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\figifq B).

>>>>

\label{fig:across}
\end{center}
\end{figure}
<!-- TODO AB: To me it is more intuitive that the darker, hotter colors would
represent higher values. Consdier reversing the color scale to go from red
(highest # of permit holders) to yellow (lowest #).  -->

@@

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given strategy (set of permits) is more
variable (Fig. \ref{fig:within}). After accounting for fishing effort and
changes in annual average revenue for fishers with the same set of permits,
specializing tends to be associated with increased revenue but also increased
variability (Fig. \ref{fig:within}; Figs S\figfe, S\figre, S\figmirror). <!--
TODO LP: effort is endogenous? --> On average, there is a ~0.5% increase in the
year-to-year revenue ratio per 1% decrease in species diversity, and across
strategies weighted equally, `r g2_dens`% of the probability density supports
a positive relationship between specialization and revenue. However, when
not controlling for effort, the average effect of specializing on revenue
becomes more neutral (Fig. S\fignoeffort).

@@

Changing (increasing or decreasing) an individual's fished species diversity
within the constraints of a strategy tends to be associated with greater
expected variability or uncertainty in year-to-year revenue (Fig.
\ref{fig:within} strategies above zero; Figs. S\figfe, S\figre, S\figmirror).
This effect was strongest for individuals with a halibut and sablefish permit.
Individuals with this strategy experienced a ~2% increase in variability for
a 1% change in the year-to-year ratio of species diversity (Figs
\ref{fig:within}, S\figmirror). 
<!-- Becoming more generalized in species diversity -->
<!-- also leads to increased revenue variability (Fig. S\figmirror A), suggesting -->
<!-- that the act of changing the number of species fished for a given set of permits -->
<!-- is a contributor to increased variability of revenue. -->

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery 
quota (IFQ) management in 1995, which potentially confounds our estimates with a
major regulatory change. Therefore, we refit our models allowing all 
strategy-level effects involving halibut and sablefish permits to vary 
separately before and after the introduction of IFQs. The introduction of IFQs 
was associated with a reduction in revenue variability of ~20--30% for
individuals with only halibut or sablefish permits (Fig. S\figifq A).
<!-- TODO AH: We need to note that the population changed -->
Furthermore, for individuals within most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\figifq B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\figifq B).

### 2017-01-27 portfolio/text/supp.Rnw
Order figs; edits

\clearpage
% TODO: AB: I suggest 2 additional columns: 1) potential species that could be harvested under each permit strategy, 2) number of unique permits contained within each strategy. This would really help to show how much flexibility someone within each permit strategy might have.
\begin{table}[h!]
\footnotesize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes.}
  \label{tab:strategies}
  \begin{tabular}{lll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represents strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error. (TODO symbols need to be updated)}
\label{fig:fe}
\end{center}
\end{figure}

@@

% TODO: tweak labels to fit
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to one's strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

% TODO: all figs referenced?

>>>>

\begin{table}[h!]
\footnotesize
  \centering
  \caption{Labels and descriptions of unique fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes.}
  \label{tab:strategies}
  \begin{tabular}{lll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to one's strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represent strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@
